`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-03 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/01_reference-aggregation.Rmd
WIP path updates

celltype_df <- readRDS(sce_file) |>
  colData() |>
  tibble::as_tibble() |>
  dplyr::select(
    barcodes,
    consensus_annotation = consensus_celltype_annotation
  )
```

@@

aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "aggregated",
    glue::glue("{params$library_id}_singler-annotations.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "aggregated")

non_aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "non-aggregated",
    glue::glue("{params$library_id}_singler-annotations.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "non-aggregated")
```

>>>>

sce_df <- readRDS(sce_file) |>
  scuttle::makePerCellDF() |>
  dplyr::select(
    barcodes,
    consensus_annotation = consensus_celltype_annotation,
    UMAP1 = UMAP.1,
    UMAP2 = UMAP.2
  )
```

@@

aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "aggregated",
    glue::glue("{params$library_id}_singler-result.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "aggregated")

non_aggr <- readr::read_rds(
  file.path(
    results_dir,
    params$sample_id,
    "not-aggregated",
    glue::glue("{params$library_id}_singler-result.rds")
  )
) |>
  as.data.frame() |>
  tibble::rownames_to_column("barcodes") |>
  dplyr::mutate(ref_type = "not-aggregated")
```
